Title

### 2018-07-30 thesis/paper/paper.tex
Added naive inequality

\todo[inline]{How are the three numbers weighted? Or do I determine that in evaluation?}

>>>>

\todo[inline]{How are the three numbers weighted? Or do I determine that in evaluation?}
\subsubsection{Naive}
The naive approach would be to to simply add all possible combinations:
\begin{equation*}
\forall x, y \in E, x \ne y \text{ add } \text{unequalEDB}(x, y)
\end{equation*}.
This can be easily improved using the inverse and adding the following rule:
\begin{equation}\label{equ_inverse}
\text{unequal}(X, Y) \leftarrow \text{unequal}(Y, X)
\end{equation}
The it is sufficient to add each combinations once if disregarding their order:
\begin{equation*}
\forall x, y \in E, x < y \text{ add } \text{unequalEDB}(x, y)
\end{equation*}.

The naive approach with inverse would result in \(f(n) = \binom{n}{2}\) EDB facts, \(r(n) = 1\) additional rule and \(m(n) = \binom{n}{2}\) materialized facts since equation \ref{equ_inverse} would be applied exactly once to every EDB fact.
